Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-09-21 Manuscript/manuscript.tex
Retouche petit Results-valitaion section.

In order to validate the newly developed model, ECC-lipids, 
we compared our simulation results without any ions to
NMR order parameters measurements and x-ray scattering form factors 
(Fig.~\ref{simVSexpNOions}). 
Our tail order parameters, as in the original Lipid14 model~\cite{dickson14},
match the experimental values. This is expected as the ECC model does not modify
the already highly optimized parameters of this region in Lipid14. 
\todo{The discussion about acyl chain and headgroup order parameters needs to be
  finished when the value for C2, the scale are fixed in the figure and
  size of the points are fixed in the figure.}
The headgroup order parameters computed form our new are slightly larger in the ECC-lipid model in comparison ,
which is in line with larger P-N vector angle in Fig.~\ref{OrderParameterCHANGESsurf}.
With the current data we cannot, however, conclude which is the more realistic
conformation since in both models other headgroup order parameter agrees
with experiments within error bars and other does not.
Slight changes are also observed in glycerol backbone order parameters,
bu the accuracy of both models is comparable to the state of art lipid models
available in literature \cite{ollila16}. The agreement between the x-ray scattering
form factors (Fig.~\ref{simVSexpNOions}) and the areas per molecule from simulations and experiments (Table~\ref{tab:apls}) 
confirm that the membrane structural properties are well captured. 
A structural comparison of ECC-lipids with Lipid14 can be found 
in SI along with results with other water models. 
%The optimal value for $f_\sigma$ was found by representing the overall membrane structure well
%by matching scattering form factors to experimental data~\cite{Petrache06, Kucerka08, Pabst10}.

>>>>

In order to validate the newly developed model, ECC-lipids, 
we compared our simulation results without any ions to
NMR order parameters measurements and x-ray scattering form factors 
(Fig.~\ref{simVSexpNOions}). 
Our tail order parameters, as in the original Lipid14 model~\cite{dickson14},
match the experimental values. This is expected as the ECC model does not modify
the already highly optimized parameters of this region in Lipid14. 
\todo{The discussion about acyl chain and headgroup order parameters needs to be
  finished when the value for C2, the scale are fixed in the figure and
  size of the points are fixed in the figure.
  JOE: I think this is fixed now.}
The headgroup order parameters $\alpha$ and $\beta$ and P-N vector angle are slightly larger in the ECC-lipid model in comparison to Lipid14 (Figs.~\ref{simVSexpNOions} and \ref{OrderParameterCHANGESsurf}). 
With the current data we cannot, however, conclude which is the more realistic
conformation since in both models one headgroup order parameter agrees
with experiments within error bars whereas the other does not.
Slight changes are also observed in glycerol backbone order parameters,
but the accuracy of both models is comparable to the state of art lipid models
available in literature \cite{ollila16}. The agreement between the x-ray scattering
form factors (Fig.~\ref{simVSexpNOions}) and the areas per molecule from simulations and experiments (Table~\ref{tab:apls}) 
confirm that the membrane structural properties are well captured. 
\todo{JOE: I think the following is actually in Fig.~\ref{simVSexpNOions}.}
A structural comparison of ECC-lipids with Lipid14 can be found 
in SI along with results with other water models. 
%The optimal value for $f_\sigma$ was found by representing the overall membrane structure well
%by matching scattering form factors to experimental data~\cite{Petrache06, Kucerka08, Pabst10}.
